Finch: Sparse and Structured Array Programming with Control Flow

### 2024-03-27 sections/eval.tex
Update on Overleaf.

\begin{figure}
	\includegraphics[width=\linewidth]{triangle_count_speedup_over_duckdb.png}
    \caption{Performance of Finch on triangle counting.}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{elementwise_speedup_over_duckdb.png}
    \caption{Performance of Finch on elementwise (A+B)*C kernel as the sparsity of C varies.}
\end{figure}

\begin{figure}
	\includegraphics[width=\linewidth]{sddmm_speedup_over_duckdb.png}
    \caption{Performance of Finch on SDDMM.}
\end{figure}

>>>>

\begin{figure}
	\includegraphics[width=.3\linewidth]{triangle_count_speedup_over_duckdb.png}
	\includegraphics[width=.35\linewidth]{sddmm_speedup_over_duckdb.png}
	\includegraphics[width=.3\linewidth]{elementwise_speedup_over_duckdb.png}
    \caption{Performance of Finch Logic for common kernels.}
\end{figure}
